Expected Dependency Pair Match: Predicting translation quality with expected syntactic structure

### 2009-08-10 mtjournal.tex
Mari's major compression and reorganization for compact.

\begin{figure}
  \centering
  \begin{tabular}{rcc}
    & \textbf{Reference} & \textbf{Hypothesis} \\
    \textbf{tree}
    & \includegraphics[scale=0.5]{dpm-example-ref} & 
    \includegraphics[scale=0.5]{dpm-example-hyp}\\
    \textbf{$dlh$ list} &
    \begin{tabular}{@{$\langle$}c@{,~}c@{,~}c@{$\rangle$}}
      the & \arclabel{\texttt{det}}  &  cat \\
      red & \arclabel{\texttt{mod}}  &  cat \\
      cat & \arclabel{\texttt{subj}} &  ate \\
      ate & \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular} & 
    \begin{tabular}{@{$\langle$}c@{,~}c@{,~}c@{$\rangle$}}
      the &      \arclabel{\texttt{det}}  &  cat \\
      cat &      \arclabel{\texttt{subj}} &  stumbled \\
      stumbled & \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular}\\
  \end{tabular}\\
%%MO: I don't think we need the P/R/F at this point in the narrative
%  Precision$_{dlh}$ is $\frac{1}{3}$ and Recall$_{dlh}$ is
%  $\frac{1}{4}$: thus $F[dlh] = \frac{2}{7}$
  \caption{Example hypothesis and reference dependency trees and the
    $dlh$ decomposition of each.}
  \label{fig:decompexample}
\end{figure}
illustrates the \emph{dependency-link-head} decomposition of a toy
dependency tree into a list of $\langle d, l, h \rangle$ tuples.  Some
members of the DPM family may apply more than one decomposition; other
good examples are the $dl$ decomposition, which generates a bag of
dependent words with outbound links, and the $lh$ decomposition, which
generates a bag of inbound link labels, with the head word for each
included. 
\begin{figure}
  \centering
    \begin{tabular}{cc}
    $dl$ & $lh$ \\
    \hline
    \begin{tabular}{@{$\langle$}c@{,~}c@{$\rangle$}}
      the & \arclabel{\texttt{det}}  \\
      cat & \arclabel{\texttt{subj}} \\
      stumbled & \arclabel{\texttt{root}} \\
    \end{tabular} &
    \begin{tabular}{@{$\langle$}c@{,~}c@{$\rangle$}}
      \arclabel{\texttt{det} } &  cat \\
      \arclabel{\texttt{subj}} &  stumbled \\
      \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular}\\
  \end{tabular}
  \caption{The $dl$ and $lh$ decompositions of the hypothesis tree in
    figure~\ref{fig:decompexample}. The items extracted here
    are individually less restrictive in their ability to match
    against reference tuples. 
%     $\precision{dl} = \frac{2}{3}$,
%     $\recall{dl} = \frac{2}{4}$, $\precision{lh} = \frac{2}{3}$,
%     $\recall{lh} = \frac{2}{4}$, so $F[dl,lh] = \frac{4}{7}$
  }
  \label{fig:decompexample2}
\end{figure}
Figure~\ref{fig:decompexample2} demonstrates the $dl$ and $lh$
decompositions for the hypothesis tree in figure~\ref{fig:decompexample}.

It is worth noting here that the $dlh$ and $lh$ decompositions (but
not the $dl$ decomposition) ``overweight'' the headwords, in that
there are $n$ elements in the resulting bag, but if a word has no
dependents it is found in the resulting bag exactly one time (in the
$dlh$ case) or not at all (in the $lh$ case).  Conversely,
syntactically ``key'' words, that are directly modified by many other
words in the tree, are included multiple times in the decomposition
(once for each inbound link).  We argue that this overcounting is a
virtue; the syntactic structure indicates which words are more
important to translate correctly.

We may not completely trust the parser's best parse.  The parser
itself, if we use a probabilistic parser, can provide an $n$-best
parse list for the translation reference and translation
hypothesis. We use the probability statistics of the list to compute
expected counts for each decomposition. Though this approach yields
partial counts, standard comparisons like precision and recall are
still valid, and using the expectations can help cope with both error
in the parser and ambiguity in the translations (reference and
hypothesis).

@@

When multiple decomposition types are used together, we may combine
these subscores in a variety of ways.  We may compute precision and
recall subscores for each decomposition separately, or, since the
results of each decomposition are of different types entirely, we may
compute them as members of one large bag for an even simpler F score.
These two approaches are equivalent when only one decomposition type
is included.  For simplicity in presentation, we use the following
notation, where $dl$ and $lh$ represent the two kinds of
decompositions described above and $\mu_h$ represents a harmonic mean:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
where $\mu_h$ represents a harmonic mean.
Dependency-based SParseval \inlinecite{roark06:sparseval} 
and the \textbf{d} approach from
\inlinecite{owczarzak07evaluatingmt} may each be understood as
$F[dlh]$, while the latter's \textbf{d\_var} method may be understood
as something close to $F[dl,lh]$.

Both of the combination methods above ($F[\cdot]$ and
$\mu_{PR}[\cdot]$) are ``naive'' in that they treat each component
score as equivalent to the next.  One further direction to explore
involves tuning (presumably on held-out data) the precision and recall
weights for each decomposition type for a later linear combination.

The possible family of metrics outlined above is quite large. In the
next section, we make explicit the range of these parameters that we
explore in this article.

\section{Experimental paradigm}
\label{sec:paradigm}
% In this section, we describe the details of the implementation and
% experimental variables explored in the experiments presented here.

@@

In this work, we use a state-of-the-art PCFG (the first stage of
\inlinecite{charniak-johnson:2005:ACL}) and context-free head-finding
rules \cite{magerman95headfinding} to generate an N-best list of
dependency trees for each hypothesis and reference translation.  We
use the parser's default (English) Wall Street Journal
training parameters.  Head-finding uses the Charniak parser's rules,
with three modifications to make the semantic (rather than syntactic)
relations more dominant in the dependency tree: prepositional and
complementizer phrases choose nominal and verbal heads respectively
(rather than functional heads) and auxiliary verbs are modifiers of
main verbs (rather than the converse).

Having constructed the dependency tree, we label the arcs as $d
\stackrel{A/B}{\to} h$, where the arc label $A/B$ between dependent
$d$ and its head $h$ is composed of $A$ (the lowest constituent-label
headed by $h$ and dominating $d$) and $B$ (the highest constituent
label headed by $d$).
\begin{figure}
  \Tree
  [.\headlabel{S}{stumbled}
    [.\headlabel{NP}{cat}
      [.\headlabel{DT}{the} the ]
      [.\headlabel{NN}{cat} cat ]
    ]
    [.\headlabel{VP}{stumbled} 
      [.\headlabel{VBD}{stumbled} stumbled ]
    ]
  ]
  \\
  \begin{center}
    \includegraphics[scale=0.6]{dpm-example-depextract}
  \end{center}
  \caption{An example constituent tree (heads of each constituent are
    listed small below the label) and the labelled dependency tree
    derived from it using the strategy described in
    section~\ref{sec:paradigm}.}
  \label{fig:depextract}
\end{figure}
For example, in figure~\ref{fig:depextract}, the S node is the lowest
node headed by \emph{stumbled} that dominates \emph{cat}, and the NP
node is the highest constituent label headed by \emph{cat}, so the arc
between \emph{cat} and \emph{stumbled} is labelled \arclabel{S/NP}.
%
This strategy is very similar to one adopted in the reference
implementation of labelled-dependency \textsc{SParseval}, and may be
considered as an approximation of the rich semantics generated by LFG
parsers \cite{cahill04lfg} or another parser with a rich semantic
representation, but using a much shallower representation.

The $A/B$ labels are not as descriptive as the LFG semantics, but they
have a similar resolution, e.g.\ the $\stackrel{S/NP}{\to}$ arc label
usually represents a subject dependent of a sentential verb.

\subsection{Dimensions of metric family}
\label{sec:metricdimensions}
In the experiments presented later in this article, we explore the
space of metrics outlined above along multiple dimensions:
\begin{description}
\item[Decompositions.] We consider syntactic decompositions of the
  following types:
  \begin{description}
  \item[dlh] $\left\langle \textrm{Dependent}, \textrm{arc Label},
      \textrm{Head}\right\rangle$ Here, every tuple includes two words
    and the dependency-label between them.
  \item[dl] $\left\langle \textrm{Dependent}, \textrm{arc Label}
      \right\rangle$ The tuple is the word plus the label of the arc
      linking it to its head; this decomposition marks how the word
      fits into its syntactic context (what it modifies).
    \item[lh] $\left\langle \textrm{arc Label}, \textrm{Head}
      \right\rangle$ Each tuple here is the dependency relation plus
      the word being modified; this decomposition implicitly marks how
      key the word is to the sentence.
    \item[dh] $\left\langle \textrm{Dependent}, \textrm{Head}
      \right\rangle$ This decomposition drops the arc from the
      dependency-pair tuple, ignoring the syntactic-role information
      implied in the arc labels.
    \item[1g,2g] These decompositions are syntactically-null.  They
      simply include each 1-gram (or 2-gram) without any syntactic
      labeling at all.  They are thus simple measures of unigram
      (bigram) precision and recall.
  \end{description}
\item[Size of $n$-best list.] Although the parser can generate
  considerably more, we consider $n$-best lists of size 1 and of size
  50.
\item[Confidence of $n$-best hypotheses.] An expectation requires a
  probability distribution over the $n$-best list, and we consider
  three options: uniform, the parser probabilities, and a flattened
  version of the parser probabilities such that $\tilde{p}(x) =
  \frac{p(x)^\gamma}{\sum_ip(i)^\gamma}$ (where $\gamma$ is a free
  parameter) to account for the fact that the parser tends to be
  over-confident.  In all cases, the probabilities are normalized to
  sum to one over the the $n$-best list, where the maximum $n$ in this
  work is 50.  The uniform distribution ($\gamma = 0$) is intended to
  be equivalent to the \cite{owczarzak07evaluatingmt}
  \textbf{d\_50} and \textbf{d\_50\_pm} measures.\endnote{
    \inlinecite{owczarzak07evaluatingmt} report no use of parse
    confidence weights, and \textbf{d\_50} and \textbf{d\_50\_pm}
    return the best-matching pair of trees rather than an aggregate
    over the tree sets.}
\item[Score combination.] We consider three possible methods for
  combining scores across decompositions, as suggested in
  section~\ref{sec:approach}:
  \begin{description}
  \item[$F\lbrack\cdot\rbrack$] treats each decomposition as
    contributing $n$ more items to the bag of tokens extracted from
    the tree, and then computes a global $F$ score.
  \item[$\mu_{PR}\lbrack\cdot\rbrack$] constructs a precision and
    recall score from each decomposition, and then does an
    evenly-weighted harmonic mean of all the component precision and
    recall scores.
  \item Tuned weight combination, like the previous $\mu_{PR}$
    combination, calculates precision and
    recall separately for each decomposition but performs a linear
    weighted combination of the resulting precision and recall scores.
    For this tuning, we note that TERp \cite{snover09terp} provides a
    tuneable system over a small number of parameters (they include,
    among others, separate cost for insertions, deletions,
    substitutions and synonyms) and an optimization algorithm that
    assigns weights to each parameter. We use the various
    decompositions' precision and recall as new parameters to the TERp
    optimizer.
  \end{description}
\end{description}

\subsection{Reference evaluation measures over parallel translations}
\label{sec:metricsreference}
For some of the experiments presented here (sections~\ref{sec:hter1}
and~\ref{sec:hter2}), we have multiple translations of the same source
segment, each from a different translation engine and each with its
own HTER score.  For these translations, reporting correlations of
metric $m$ with absolute HTER scores can conflate $m$'s power in
identifying which of two candidate translations is better with $m$'s
(and HTER's) ability to distinguish which source segments are more
difficult to translate.

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}m$ and $\bar{\mu}\textrm{HTER}$ (rather than measure
$m$ and HTER), where $\bar{\mu}$ represents mean-removal and $t_i$
represents the $i$th translation of segment $t$:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}m(t_i) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\endnote{Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment, unlike the mean-removal
  suggested in section~\ref{sec:metricsreference}. Those results are similar to
  those reported in section~\ref{sec:hter1}. However, we believe that pairwise differences
  introduce problems with the independence assumptions in the
  Pearson's $r$ tests, and we use mean-removal throughout this work
  instead.}

%% MO: Okay, but a little hard to figure out.
When reporting HTER correlations per-sentence, we use length-weighted
correlation, since unweighted correlations effectively put too much
emphasis on short sentences.  We do not weight for length for the
per-document correlations in section~\ref{sec:hter1}, because we
assume documents to be equally important (regardless of length).

@@

To explore members of the DPM metric family, we explore the
correlations of various configurations against a corpus of human
judgments of fluency and adequacy.

\subsection{Corpus}
\label{sec:facorpus}
For these experiments, we use LDC Multiple Translation Chinese corpus
parts 2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}, which are composed of
translations of written Chinese news stories.  These corpora
include multiple human judgments of fluency and adequacy for each
sentence, with each judgment using a different human judge and a
different reference translation.  Both fluency and adequacy
assessments are assigned on a five-point scale. For a rough\endnote{Our segment
  count reported in section~\ref{sec:facorpus} differs from
  \inlinecite{owczarzak07evaluatingmt}, who report 16,807 segments
  over the same corpus. We find baseline (BLEU and TER) per-segment correlations slightly
  different (BLEU$_4$ is higher here, while TER here is lower) than
  reported there as well, so the results
  presented here are not directly comparable with that paper, though
  we demonstrate similar gains over those baselines in essentially the
  same corpus.
} comparison with \inlinecite{owczarzak07evaluatingmt}, we treat
each judgment as a separate segment.
%
This treatment of this corpus yields 16,815 tuples of
$\langle$hypothesis, reference, fluency, adequacy$\rangle$.  In these
experiments, we extend this tuple with automatic scores derived from
$\langle$hypothesis, reference$\rangle$ and examine the per-segment
correlations\endnote{The independence of the translation segments in
  the Multiple Translation Corpus described in
  section~\ref{sec:facorpus} is questionable, since the same
  hypothesis translations are used in multiple items, but for the sake
  of methodological comparison with prior work, this strategy is
  preserved.}  between those automatic scores and the arithmetic mean
of the fluency and adequacy measures.

\subsection{Exploring decompositions}
We begin by comparing some of the simplest DPM measures to baseline
measures case-sensitive BLEU (4-grams, with add-one smoothing) and
TER.  For these first experiments, we consider only the 1-best parse
($n=1$).
\begin{table}
  \caption{Comparing $dl,lh$ to $dlh$ and baseline per-segment correlations with
    human fluency and adequacy judgments.}
  \label{tab:facorr:subgraphs}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$|r|$} \\
    \hline
    $F[dl,lh]$ &   0.226 \\
    % # +1 smoothing
    BLEU$_4$ &   0.218 \\
    $F[dlh]$ &     0.185 \\
    TER &      0.173 \\
    \hline
  \end{tabular*}
\end{table}
In table~\ref{tab:facorr:subgraphs} we see that using the
partial-label $dl,lh$ decomposition has a better per-segment correlation with the
fluency/adequacy scores than TER or BLEU$_4$.  These results confirm,
with a PCFG, what \inlinecite{owczarzak07evaluatingmt} found with
an LFG parser: that partial-dependency matches are better correlated
with human judgments than full-dependency links.

In table~\ref{tab:facorr:combinations}, we compare among several other
members of the DPM family. 
 \begin{table}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[1g,2g]$            & 0.227 \\
    $\mu_{PR}[1g,2g]$            & 0.215 \\
%    $F[1g,dl,dlh]$        & 0.227 \\
    \rlcline{1-1} \rlcline{2-2}
    $F[dl,lh]$            &  0.226 \\
    $\mu_{PR}[dl,lh]$      &  0.208 \\
    \hline
  \end{tabular*}
  \caption{Correlation with human fluency/adequacy judgments. Comparing combination methods $F[\cdot]$ and
    $\mu_{PR}[\cdot]$, and comparing the $1g,2g,dl,lh$ decomposition
    with the $dl,lh$ decomposition and other decompositions.}
  \label{tab:facorr:combinations}
\end{table}
Here, we find that combining the decompositions naively in $F[\cdot]$
(before computing precision and recall) has a better $r$ than the
harmonic mean of precision and recall subscores in $\mu_{PR}[\cdot]$.
In fact, $F[\cdot]$ measures always outperform the BLEU baseline (from
table~\ref{tab:facorr:subgraphs}), and $\mu_{PR}[\cdot]$ measures are
never better than BLEU.
We also see that we can combine the benefits of string-local $n$-grams
($F[1g,2g]$) with the benefits of dependency information ($F[dl,lh]$)
for a further improved correlation with human judgment, with the best
correlation in $F[1g,2g,dl,lh]$. Including progressively larger chunks
of the dependency graph with $F[1g,dl,dlh]$ (not shown in table, but inspired by
the BLEU$_k$ idea of progressively larger $n$-grams) does not seem to
be an improvement over $F[dl,lh]$.

% (too many chances for zeroes?)

\subsection{Exploring parse expectations}

>>>>

\begin{figure}
  \centering
  \begin{tabular}{rcc}
    & \textbf{Reference} & \textbf{Hypothesis} \\
    \textbf{tree}
    & \includegraphics[scale=0.5]{dpm-example-ref} & 
    \includegraphics[scale=0.5]{dpm-example-hyp}\\
    \textbf{$dlh$ list} &
    \begin{tabular}{@{$\langle$}c@{,~}c@{,~}c@{$\rangle$}}
      the & \arclabel{\texttt{det}}  &  cat \\
      red & \arclabel{\texttt{mod}}  &  cat \\
      cat & \arclabel{\texttt{subj}} &  ate \\
      ate & \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular} & 
    \begin{tabular}{@{$\langle$}c@{,~}c@{,~}c@{$\rangle$}}
      the &      \arclabel{\texttt{det}}  &  cat \\
      cat &      \arclabel{\texttt{subj}} &  stumbled \\
      stumbled & \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular}\\
  \end{tabular}\\
%%MO: I don't think we need the P/R/F at this point in the narrative
%  Precision$_{dlh}$ is $\frac{1}{3}$ and Recall$_{dlh}$ is
%  $\frac{1}{4}$: thus $F[dlh] = \frac{2}{7}$
  \caption{Example hypothesis and reference dependency trees and the
    $dlh$ decomposition of each.}
  \label{fig:decompexample}
\end{figure}

\begin{figure}
  \centering
    \begin{tabular}{cc}
    $dl$ & $lh$ \\
    \hline
    \begin{tabular}{@{$\langle$}c@{,~}c@{$\rangle$}}
      the & \arclabel{\texttt{det}}  \\
      cat & \arclabel{\texttt{subj}} \\
      stumbled & \arclabel{\texttt{root}} \\
    \end{tabular} &
    \begin{tabular}{@{$\langle$}c@{,~}c@{$\rangle$}}
      \arclabel{\texttt{det} } &  cat \\
      \arclabel{\texttt{subj}} &  stumbled \\
      \arclabel{\texttt{root}} &  $<$root$>$ \\
    \end{tabular}\\
  \end{tabular}
  \caption{The $dl$ and $lh$ decompositions of the hypothesis tree in
    figure~\ref{fig:decompexample}. The items extracted here
    are individually less restrictive in their ability to match
    against reference tuples. 
%     $\precision{dl} = \frac{2}{3}$,
%     $\recall{dl} = \frac{2}{4}$, $\precision{lh} = \frac{2}{3}$,
%     $\recall{lh} = \frac{2}{4}$, so $F[dl,lh] = \frac{4}{7}$
  }
  \label{fig:decompexample2}
\end{figure}

It is worth noting here that the $dlh$ and $lh$ decompositions (but
not the $dl$ decomposition) ``overweight'' the headwords, in that
there are $n$ elements in the resulting bag, but if a word has no
dependents it is found in the resulting bag exactly one time (in the
$dlh$ case) or not at all (in the $lh$ case).  Conversely,
syntactically ``key'' words, that are directly modified by many other
words in the tree, are included multiple times in the decomposition
(once for each inbound link).  This ``overcounting'' leverages
syntactic indications of which words are more
important to translate correctly (e.g., ``Basra'' in the
example).

A probabilistic parser provides confidences associated with parses
in an $n$-best list, which we can use to compute
expected counts for each decomposition in both the reference and
hypothesized translations. The expected counts lead to partial matches
which are used to compute precision and recall as weighted counts.
Using the expectations can help cope with both error
in the best parse and ambiguity in the translations (reference and
hypothesis).

@@

%%MO: I think that it is important to keep because of some of the comparisons
%% you make, so I will try to just compress

When multiple decomposition types are used together, we may combine
these subscores in a variety of ways. Here, we experiment with using
two variations of a harmonic mean:
computing precision and recall over all
decompositions as a group (giving a single precision and recall number)
vs.\ computing precision and recall separately for each decomposition.
We distinguish between these using the notation:
\begin{eqnarray}
  \label{eq:fprmeans}
  F[dl,lh] & = &
  \mu_h \left( \precision{dl \cup lh},
    \recall{dl \cup lh} \right) \\
  \mu_{PR}[dl,lh]  & = & \mu_h \left( \precision{dl},
    \recall{dl}, \precision{lh}, \recall{lh} \right)    
\end{eqnarray}
where $\mu_h$ represents a harmonic mean.
Dependency-based SParseval \inlinecite{roark06:sparseval} 
and the \textbf{d} approach from
\inlinecite{owczarzak07evaluatingmt} may each be understood as
$F[dlh]$, while the latter's \textbf{d\_var} method may be understood
as something close to $F[dl,lh]$.
%
Both the combination methods $F$ and
$\mu_{PR}$ are ``naive'' in that they treat each component
score as equivalent to the next.  When we introduce syntactic/paraphrasing
features, we will move to a weighted combination.

%%MO: actually the next section does more than this, and this sentence is
%% essentially repeated later, so I deleted it here
%The possible family of metrics outlined above is quite large. In the
%next section, we make explicit the range of these parameters that we
%explore in this article.

%%MO: I changed the title, since I usually put corpus in ``paradigm''. You 
%% are really just talking about implementation here

\section{Experimental implementation}
\label{sec:paradigm}
% In this section, we describe the details of the implementation and
% experimental variables explored in the experiments presented here.

@@

In this work, we use a state-of-the-art PCFG (the first stage of
\inlinecite{charniak-johnson:2005:ACL}) and context-free head-finding
rules \cite{magerman95headfinding} to generate an N-best list of
dependency trees for each hypothesis and reference translation.  We
use the parser's default (English) Wall Street Journal
training parameters.  Head-finding uses the Charniak parser's rules,
with three modifications to make the semantic (rather than syntactic)
relations more dominant in the dependency tree: prepositional and
complementizer phrases choose nominal and verbal heads respectively
(rather than functional heads) and auxiliary verbs are modifiers of
main verbs (rather than the converse). These changes capture the
fact that main verbs are more important for adequacy in translation, as
illustrated by the functional equivalence of ``have also closed'' vs.\ 
``also closed'' in the example in section~\ref{sec:approach}.

Having constructed the dependency tree, we label the arc between dependent
$d$ and its head $h$ as $A/B$ when $A$ is the lowest constituent-label
headed by $h$ and dominating $d$ and $B$ is the highest constituent
label headed by $d$).
%
For example, in figure~\ref{fig:depextract}, the S node is the lowest
node headed by \emph{stumbled} that dominates \emph{cat}, and the NP
node is the highest constituent label headed by \emph{cat}, so the arc
linking \emph{cat} to \emph{stumbled} is labelled $S/NP$.
%
This strategy is very similar to one adopted in the reference
implementation of labelled-dependency \textsc{SParseval} \cite{roark06:sparseval}, and may be
considered as a shallow approximation of the rich semantics generated by LFG
parsers \cite{cahill04lfg}.
%
The $A/B$ labels are not as descriptive as the LFG semantics, but they
have a similar resolution, e.g.\ the $S/NP$ arc label
usually represents a subject dependent of a sentential verb.

\begin{figure}
  \Tree
  [.\headlabel{S}{stumbled}
    [.\headlabel{NP}{cat}
      [.\headlabel{DT}{the} the ]
      [.\headlabel{NN}{cat} cat ]
    ]
    [.\headlabel{VP}{stumbled} 
      [.\headlabel{VBD}{\it stumbled} stumbled ]
    ]
  ]
  \\
  \begin{center}
    \includegraphics[scale=0.6]{dpm-example-depextract}
  \end{center}
  \caption{An example constituent tree (heads of each constituent are
    listed below the label) and the labelled dependency tree
    derived from it.}
  \label{fig:depextract}
\end{figure}

%%MO: I added this though reviewers didn't ask for it, since I thought that
%% this is actually a tricky concept plus the flattening description should
%% really go here. You might want to change the example
For the cases where we have N-best parse hypotheses, we use the associated
parse probabilities (or confidences) to compute expected
counts. The sentence will then be represented with more tuples,
corresponding to alternative analyses. For example, if the N-best
parses include two different roles for dependent ``Basra'', then two
different $dl$ tuples are included, each with the weighted count that is the
sum of the confidences of all parses having the respective role.\endnote{
    The use of expectations with N-best parses is different from 
    \textbf{d\_50} and \textbf{d\_50\_pm} in \cite{owczarzak07evaluatingmt}
    in that the latter uses the best-matching pair of trees rather than an 
    aggregate over the tree sets and they do not use parse
    confidences.}
The parse confidence $\tilde{p}$ is normalized so that the
N-best confidences sum to one. Because the parser is overconfident, we
explore a flattened estimate: $\tilde{p}(k) =
\frac{p(k)^\gamma}{\sum_ip(i)^\gamma},$ where $k,i$ index the parse and
$\gamma$ is a free parameter.

%%MO: I took this out, since this is not true now that you have more info
%The uniform distribution ($\gamma = 0$) is equivalent to the \cite{owczarzak07evaluatingmt}
%  \textbf{d\_50} and \textbf{d\_50\_pm} measures.

\subsection{Dimensions of metric family}
\label{sec:metricdimensions}
In the experiments presented later in this article, we explore the
space of metrics outlined above along three dimensions:
\begin{description}
\item[Decompositions.] We compute precision and recall of:
  \begin{description}
  \item[dlh] $\left\langle \textrm{Dependent}, \textrm{arc Label},
      \textrm{Head}\right\rangle$ -- full triple
  \item[dl] $\left\langle \textrm{Dependent}, \textrm{arc Label}
      \right\rangle$ --  marks how the word
      fits into its syntactic context (what it modifies)
    \item[lh] $\left\langle \textrm{arc Label}, \textrm{Head}
      \right\rangle$ --  implicitly marks how
      key the word is to the sentence
    \item[dh] $\left\langle \textrm{Dependent}, \textrm{Head}
      \right\rangle$ -- drops syntactic-role information.
    \item[1g,2g] -- simple measures of unigram
      (bigram) precision and recall.
  \end{description}
\item[Parser variations.] When using more than one parse, we explore:
  \begin{description}
  \item[Size of $n$-best list.] 50 (as in \cite{owczarzak07evaluatingmt})
  \item[Parse confidence.] The distribution flattening
    parameter is varied from $\gamma=0$ (uniform distribution) to $\gamma=1$
    (no flattening).
%%MO: I recall that you tried more than one possible gamma in the middle
%% range to get the 0.25 value, so I think it is misleading to say you looked
%% at 3 cases.
  \end{description}
\item[Score combination.] Global $F$ vs.\ component harmonic mean $\mu_{PR}$.
\end{description}

@@

We explore various configurations of the DPM by assessing the results
against a corpus of human judgments of fluency and adequacy,
specifically the LDC Multiple Translation Chinese corpus parts
2~\cite{LDC03MTC2} and 4~\cite{LDC06MTC4}, which are composed of
translations of written Chinese news stories.  These corpora include
multiple human judgments of fluency and adequacy for each sentence
(assigned on a five-point scale), with each judgment using a different
human judge and a different reference translation.  For a
rough\endnote{Our segment count differs from
  \inlinecite{owczarzak07evaluatingmt}, who report 16,807 segments
  over the same corpus, so the results presented here are not directly
  comparable with that paper. As a result, the baseline (BLEU and TER)
  per-segment correlations differ slightly (BLEU$_4$ is higher here,
  while TER here is lower), but the trends in gains over those
  baselines are very similar.  } comparison with
\inlinecite{owczarzak07evaluatingmt}, we treat each judgment as a
separate segment, which yields 16,815 tuples of $\langle$hypothesis,
reference, fluency, adequacy$\rangle$.  We compute the per-segment
correlations\endnote{The use of the same hypothesis translations in
  multiple comparisons in the Multiple Translation Corpus means that
  scored segments are not strictly independent, but for methodological
  comparison with prior work, this strategy is preserved.}
%
The baselines for comparison are case-sensitive BLEU (4-grams, with add-one smoothing) and TER.

Considering only the 1-best parse, we compare DPM with different
decompositions to the baseline measures.
Table~\ref{tab:facorr:subgraphs} shows that all decompositions except
$[dlh]$ have a better per-segment correlation with the
fluency/adequacy scores than TER or BLEU$_4$. Dependencies $[dl,lh]$
and string-local n-grams $[1g,2g]$ give similar results, but the
combination gives further improvement.  The results also confirm, with
a PCFG, what \inlinecite{owczarzak07evaluatingmt} found with an LFG
parser: that partial-dependency matches are better correlated with
human judgments than full-dependency links. Including progressively
larger chunks of the dependency graph with $F[1g,dl,dlh]$, inspired by
the BLEU$_k$ idea of progressively larger $n$-grams, did not give an
improvement over $[dl,lh]$.  $F$ gives substantially better results than
$\mu_{PR}$, which is never better than BLEU for these decompositions.

\begin{table}
  \caption{Per-segment correlation with
    human fluency/adequacy judgments of baselines and different decompositions.}
  \label{tab:facorr:subgraphs}
  \begin{tabular*}{2.5in}{lr}
    \hline
    metric  &    \multicolumn{1}{c}{$|r|$} \\
    \hline
    $F[1g,2g,dl,lh]$      &  0.237 \\
    $F[1g,2g]$            & 0.227 \\
    $F[dl,lh]$ &   0.226 \\
    % # +1 smoothing
    BLEU$_4$ &   0.218 \\
    $F[dlh]$ &     0.185 \\
    TER &      0.173 \\
    \hline
  \end{tabular*}
\end{table}

%In table~\ref{tab:facorr:combinations}, we compare combination methods
%for different decompositions, finding that $F$ consistently outperforms
%$\mu_{PR}$ as well as the BLEU basedline (from table~\ref{tab:facorr:subgraphs})$\mu_{PR}$ measures are never better than BLEU.

% \begin{table}
%  \begin{tabular*}{2.5in}{lr}
%    \hline
%    metric  &    \multicolumn{1}{$r$} \\
%    \hline
%    $F[1g,2g,dl,lh]$      &  0.237 \\
%    $\mu_{PR}[1g,2g,dl,lh]$ &  0.217 \\
%    \rlcline{1-1} \rlcline{2-2}
%    $F[1g,2g]$            & 0.227 \\
%    $\mu_{PR}[1g,2g]$            & 0.215 \\
%    $F[1g,dl,dlh]$        & 0.227 \\
%    \rlcline{1-1} \rlcline{2-2}
%    $F[dl,lh]$            &  0.226 \\
%    $\mu_{PR}[dl,lh]$      &  0.208 \\
%    \hline
%  \end{tabular*}
%  \caption{Per-segment correlation with human fluency/adequacy judgments of different combination methods and decompositions.}
%  \label{tab:facorr:combinations}
%\end{table}

Table~\ref{tab:facorr:multiparse} shows the impact of using N-best
parses for different decompositions.
For the $n=50$ cases, we set $\gamma=0$ to assign uniform
probabilities, which was slightly better than $\gamma=1$.
%%MO: I want to take this out, since it really isn't a comparison
%% if they are using the best match.  I recalled that 0 was better than 
%% 1 -- change if not
%to compare as closely as possible
%to \inlinecite{owczarzak07evaluatingmt}, which includes a
%\textbf{d\_var\_50} measure with 50-best parses, with ranks but no
%weights.  
While not all of these differences are significant, there is a
consistent trend of correlation $r$ improving with 50 vs. 1 parse.  Tuning
experiments find that increasing $\gamma$ to 0.25 can increase the $r$
reported here for $F[1g,2g,dl,lh]$ (but insignificantly).

 \begin{table}
  \begin{tabular*}{2.5in}{lrr}
    \hline
    metric  & \multicolumn{1}{c}{$n$} &  \multicolumn{1}{c}{$r$} \\
    \hline
    $F[1g,2g,dl,lh]$      & 50 &  0.239 \\
    $F[1g,2g,dl,lh]$      &  1 &  0.237 \\
    \rlcline{1-2}\rlcline{3-3}
    $F[1g,dl,lh]$            &  50 & 0.237 \\
    $F[1g, dl,lh]$            &  1 & 0.234 \\
    \rlcline{1-2}\rlcline{3-3}
    $F[dl,lh]$            &  50 & 0.234 \\
    $F[dl,lh]$            &  1 & 0.226 \\
    \hline
  \end{tabular*}
  \caption{Per-segment correlation with human fluency/adequacy judgments
  comparing $n=1$ vs.\ 50 parses for different decompositions.}
  \label{tab:facorr:multiparse}
\end{table}

In summary, exploring a number of
variants of the DPM metric against an average fluency/adequacy
judgment leads to a best-case of:
\begin{displaymath}
  \mbox{EDPM} = F[1g,2g,dl,lh], n=50, \gamma=0.25
\end{displaymath}
We use this configuration in experiments assessing correlations with HTER.

\section{Correlating EDPM with HTER}
\label{sec:hter1}
In this section, we compare EDPM to baseline metrics in terms of
document- and segment-level correlation with HTER scores using the
GALE 2.5 translation corpus.  The corpus includes system translations
into English from three sites, all of which use system combination to
integrate results from several systems, some phrase-based and some
that use syntax on either the source or target side. No system
provided system-generated parses.
%
The source data comprises Arabic and Chinese in four
genres: \texttt{bc} (broadcast conversation), \texttt{bn} (broadcast
news), \texttt{nw} (newswire), and \texttt{wb} (web text), with corpus
sizes shown in table~\ref{tab:galestats}.
The corpus includes one English reference translation
\cite{gale08phase2_5references} for each sentence and a system
translation for each of the three systems. Additionally,
each of the system translations has a
corresponding human-targeted reference aligned at the sentence level,
and an associated so we have available the HTER score at
both the sentence and document level.
